---
title: "Fix the title"
author: "Neeraj Thokala"
date: "6/23/23"
output: 
    html_notebook
---

### Question 1: Subsetting

#### Select the element in 10th row and 5th column in `iris` dataset

```{r}
data(iris)
iris[10,5]
```
 

#### Select the Species column in `iris` dataset and print the last 5 rows of that column
```{r}
data_frame<-iris$Species
print(data_frame.tail(5))
```


#### What is the average Sepal Length of flowers with Petal widths greater than 1? 

```{r}
mean(subset(iris, Petal.Width > 1))

```

### Question 2: For Loops

#### Write a `for` loop that iterates over the numbers 1 to 10. If the number less than 5 print the multiple of 3 (multiply the number by 3), and if the number is greater than or equal to 5 print the multiple of 2 (multiply the number by 2). 

```{r}
for (i in 1:10)
{
    if (i < 5)
    {
        print(i * 3)
    }
    else (i >= 5)
    {
        print(i * 2)
    }
}
```

### Question 3: While loops

#### Write a `while` loop that prints out random normal numbers with mean equal 1 and standard deviation 2 (use rnorm()) but stops (breaks) if you get a number bigger than 3. Do not change the value inside set.seeed.
```{r}
set.seed(184)
while(1){ 
n <- rnorm(1, 0, 1) 
if(n>1){ 
break 
}
print(n) 
}
```

### Question 4: for loops in data tables

#### Use a nested for loop that produces the following data frame. Name the dataframe  `Counting` and the variables (columns)  V1, V2, V3, and V4.  (There are 3 loops). 

Hint: First identify the pattern(s) in the table before you create the for loop.

| V1 | V2 | V3 | V4 |  
|:-- |:-- |:-- |:-- |
| 1 | 2 | 3 | 4 |  
| 2 | 3 | 4 | 5 |  
| 3 | 4 | 5 | 6 |  

```{r}
Counting<-NULL # define the data frame to be a Null
for (i in 1:3){ 
  row<-c() 
  for (j in 1:4){ 
    row[j]<-j+(i-1) 
    
  }
  Counting<-rbind(Counting,data.frame(V1=row[1],V2=row[2],V3=row[3],V4=row[4]))  
}
Counting 
```

### Question 5: user defined functions

#### 5A) Complete the following user define function to generate `n` random normal numbers with a given mean and standard deviation and plot a histogram of it. Do not change  the seed number in set.seed. You can use the function `hist` to plot the histogram.  

##### 5B) Then call the function to generate 1000 random normal numbers with mean 0 and standard deviation 1 and plot a histogram of it.

```{r}
set.seed(184)
plotNormal<-function(repitions,mean,sd){
  r<-rnorm(repitions,mean,sd) 
  return(r) # return the numbers
}

r<-plotNormal(1000,0,1)
hist(r,breaks=20,col='green') 

```

##### Extra Credit: 

Repeat parts 5A and 5B, and add 

1. A title that say "Histogram from a Normal(`mean`, `sd`) Distribution", but the user given values of `mean` and `sd`.
2. an argument to change the color of the histogram.  

Call the function to generate 1000 random normal numbers with mean 0 and standard deviation 1 and plot a histogram. Make the bins blue.

```{r}

set.seed(184)
plotNormal<-function(repitions,mean,sd){
  r<-rnorm(repitions,mean,sd) 
  return(r) # return the numbers
}

r<-plotNormal(1000,0,1)
hist(r,breaks=20,col='blue') 

```
